Software Citation Principles

### 2016-03-02 sc-principles/software-citation-principles.tex
adding comments about group and goal based on comment from James

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members (see Appendix~\ref{app:wg_members}), and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

>>>>

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015, with the following mission statement:

\begin{quote}
The software citation working group is a committee that will leverage the perspectives of a variety of existing initiatives working on software citation to produce a consolidated set of citation principles in order to encourage broad adoption of a consistent policy for software citation across disciplines and venues. The working group will review existing efforts and make a set of recommendations. These recommendations will be put up for endorsement by the organizations represented by this group and others that play an important role in the community.

The group will produce a set of principles, illustrated with working examples, and a plan for dissemination and distribution. This group will not be producing detailed specifications for implementation although it may review and discuss possible technical solutions.\end{quote}

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015, and then in June began work, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

The principles in this document should guide further development of software citation mechanisms and system, and the reader should be able to look at any particular example of software citation and see if it meets the principles.
